Capstone Movielens Report

### 2025-05-11 reports/capstone-movielens-report.draft4.Rmd
Draft report development: function `model.tune.param_range`, cross reference to the `tune.model_param` fuction description in `fn_tune.test.param_value` parameter description fixed.

###### Parameters
\
####### loop_starter 
\
A numeric vector of the form `c(start, end, dvs)`, where `start` and `end` are the endpoints of the interval on which the parameter value that minimizes `RMSE` is sought.
`dvs` is a divisor for splitting the interval to transform it into a sequence of values among which the value that minimizes `RMSE` is sought.
For this purpose, the sequence step is calculated as follows:
$$
step = \frac{end - start}{dvs}
$$

@@

To improve performance, the algorithm caches intermediate results in the file system. This parameter specifies the path to the directory where the cache files are saved.

@@

This is a helper function name that is passed to the same-named parameter of the [tune.model_param] function that is called internally during the execution (see the [description of the `tune.model_param` function](#func.tune.model_param) above).

>>>>

###### Parameters
\
####### loop_starter 
\

A numeric vector of the form `c(start, end, dvs)`, where `start` and `end` are the endpoints of the interval on which the parameter value that minimizes `RMSE` is sought.
`dvs` is a divisor for splitting the interval to transform it into a sequence of values among which the value that minimizes `RMSE` is sought.
For this purpose, the sequence step is calculated as follows:
$$
step = \frac{end - start}{dvs}
$$

@@

To improve performance, the algorithm caches intermediate results in the file system. This parameter specifies the path to the directory where the files are cached.

@@

This is a helper function name that is passed to the same-named parameter of the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during the execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).

### 2025-05-11 reports/capstone-movielens-report.draft4.tex
Draft report development: function `model.tune.param_range`, cross reference to the `tune.model_param` fuction description in `fn_tune.test.param_value` parameter description fixed.

\hfill\break
\#\#\#\#\#\#\# loop\_starter\\
A numeric vector of the form \texttt{c(start,\ end,\ dvs)}, where
\texttt{start} and \texttt{end} are the endpoints of the interval on
which the parameter value that minimizes \texttt{RMSE} is sought.
\texttt{dvs} is a divisor for splitting the interval to transform it
into a sequence of values among which the value that minimizes
\texttt{RMSE} is sought. For this purpose, the sequence step is
calculated as follows: \[
step = \frac{end - start}{dvs}
\]

@@

This is a helper function name that is passed to the same-named
parameter of the {[}tune.model\_param{]} function that is called
internally during the execution (see the
\hyperref[func.tune.model_param]{description of the
\texttt{tune.model\_param} function} above).

>>>>

\hfill\break
\#\#\#\#\#\#\# loop\_starter\\

A numeric vector of the form \texttt{c(start,\ end,\ dvs)}, where
\texttt{start} and \texttt{end} are the endpoints of the interval on
which the parameter value that minimizes \texttt{RMSE} is sought.
\texttt{dvs} is a divisor for splitting the interval to transform it
into a sequence of values among which the value that minimizes
\texttt{RMSE} is sought. For this purpose, the sequence step is
calculated as follows: \[
step = \frac{end - start}{dvs}
\]

@@

This is a helper function name that is passed to the same-named
parameter of the
\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R\#L116}{tune.model\_param}
function that is called internally during the execution (see the
description of the \texttt{tune.model\_param} function
\hyperref[func.tune.model_param]{above}).
